\chapter{Alumni Programming}

  The Alumni Relations Committee is responsible for the organization and administration of alumni programming and outreach. Its primary tasks include organization of alumni-involved parties, such as the Christmas Party in the Fall Semester and the Founder's Day Party in Spring Semester. It also keeps the alumni database up to date and coordinates news releases with our semester alumni newsletter. A new initiative that the alumni relations committee has spearheaded this year is coordinating alumni visits to chapter. Specifically, this is achieved by having alumni sign up for dates to visit our chapter ahead of time on a monthly rotating basis. This has led to a 5X increase in alumni participation in the chapter as a whole thanks to offering more flexible scheduling.

  \section*{OX Roast}
    Over the past year, we have held a number of alumni oriented events with strong alumni participation. The largest of these was our annual OX roast, which was held on October 18th, 2014. This event, which has a long history behind it, serves as one of the chapter’s largest events. It takes place during homecoming, and it is where we showcase the chapter accomplishments from the past year with parents, alumni, and a representative from IHQ. This year we had the pleasure of hearing Brother Couch, our Grand Chapter Vice President, speak. In addition, during OX roast we held our big brother ceremony and the OX memorial ceremony. Both of these ceremonies allow us to share more public traditions with our significant others, alumnus brothers, and friends.
    
  \section*{Christmas Party and Founder's Day}
    We also held a number of smaller events. On December 5, 2014 the actives and alumni celebrated the Christmas season with a joint Christmas party. The highlights included Professor Drushel’s delicious homemade root beer, a small active/alumni brass band playing Christmas carols, and a Secret Santa exchange. \\
    
    We celebrate our founder’s day every year with a sit down dinner with our alumni. This year, we dedicated our new chapter museum to alumnus Brother Drushel and alumnus Brother Divincenzo. We also found a manuscript of a radio play that describes the first chapter meeting with Fredrick Norton Freeman and Arthur Chase. We performed it in a manner that made it feel like it was a traditional radio drama.
    
  \section*{Alumni Communication}
    The main method of communication between the active chapter and alumni is our alumni email list. This keeps alumni informed of all chapter events. The list contains roughly half of the chapter’s alumni, and we use it communicate with our alumni, and the alumni use it to communicate with each other. \\

    Over the past year, alumni have shared some amazing news, including the introduction of several adorable children, and shared with the actives some fantastic advice on how to get a job. The chapter also publishes a yearly newsletter, maintains a website, and Facebook page. These are used to publish news of upcoming events. A separate, private Facebook group is used for discussions as well.
    
  \section*{Alumni Board}
    Our chapter advisors serve as an integral part of our chapter. Our Alumni Housing Corporation, led by Robert Divincenzo (nicknamed ``D.V.``), meets with the undergrads regularly and ensures that we have a house to live in and sees to our needs. We are in the midst of contract renegotiations with the University, and the housing corporation continues to do an incredible job at ensuring we get fair terms for the beautiful home we have. \\

    In the past year, we replaced our Alumni Adviser, Dan Myers, who wanted to take on a smaller role due to work commitments at his law firm. He was replaced by brother Daniel Neumann. Dan Myers now serves as our legal advisor. Thus far, Dan Neumann has done an excellent job, complementing the work done by our Exec Adviser Matthew Richter, Financial Adviser John Boyer, Health and Safety Adviser J.J. Moffitt, Housing Corporation Chair D.V., and our Faculty Adviser Richard Drushel. Drushel, in particular, is extremely active in our chapter, and he attends almost every single chapter meeting during the semester. He also meets with the President on a bi-weekly basis to discuss chapter operations. Our advisers are tireless in their efforts for the fraternity, and we appreciate all of their efforts to push us to reach our potential.
    
  \section*{Alumni Engagement}
    Our alumni have been extremely active in our ritual ceremonies, with quite a few showing up to both the public and private events and initiation ceremonies. In addition to alumni attending our Initiations, alumni ceremonies, and other public ceremonies, we have had alumni actively attend and participate in our Candidate Education Program and Member Development Program. Our alumni have provided excellent advice on topics such as personal finance, tax filing, and creating resumes. Our alumni also provide sound advice, assistance and service in other aspects of chapter operations. For example, Brother Daniel Neumann assists with the operation of the chapter web site and Brother Moffit has helped Beta Nu engage with a variety of initiatives that Greek life as a whole has adopted.  \\

    Our alumni are integral to our success, and we make every effort to recognize them. New initiatives we plan on starting include sending them hand written thank you cards each summer. Their efforts have helped us thrive and we look forward to many more years with them by our side.