\chapter{Campus Involvement}

  Our brothers are leading and participating in a variety of initiatives throughout campus. Though a large amount of our involvement throughout the campus has been highlighted in other sections, the following list summarizes more of what we do. A superscript ``1'' denotes that brothers have one or more leadership positions within an organization. A superscript ``2`` denotes that our brothers either founded the organization or are active as a president of the organization. For some organizations, we have included a short description.
    
    \subsection*{Performance Groups}
      \begin{enumerate}
      	\item Speak Easy Acapella$^1$
      	
      	\item Case Men's Glee Club$^1$
      	
      	\item CWRU Juggling
      	
      	\item Concert Choir
      	
      	\item Swing Dancing
      	
      	\item Marching Band
      	
      \end{enumerate}
      
    \subsection*{Professional Groups}
      \begin{enumerate}
      	\item Tau Beta Pi$^1$ - Engineering Honors Society
      	
      	\item Student Turning Point Society$^2$ - Leadership Honors Society for top 1\% of students
      	
      	\item Institute for Electrical and Electronics Engineers$^2$
      	
      	\item Beta Alpha Psi - Accounting Honors Society
      	
      	\item American Society of Mechanical Engineers$^2$
      	
      	\item Society of Hispanic Professional Engineers
      \end{enumerate}
      
    \subsection*{Service and Advocacy Groups}
      \begin{enumerate}
      	\item Spectrum - Organization to support people within the LGBT community
      	
	\item National Alliance on Mental Illness at CWRU$^1$
	
	\item National Alliance on Mental Illness at Greater Cleveland
	
	\item Lambda Eta Mu$^1$ - Service Honors Society
	
	\item Kids Against Hunger Cleveland$^2$
	
	\item Replay for Kids$^1$- Toy adaptations for children with disabilities
	
	\item Student Sustainability Council
	
	\item Center for Civic Engagement and Learning$^1$
	
	\item What You do Matters Summit on Hate Speech$^1$
	
	\item Sustained Dialogue Campus Network$^1$- Talk about campus issues in diverse group settings
	
	\item Order of Omega- Leadership Honors Society
	
	\item Engineering World Health$^1$
	
	\item Alpha Phi Omega$^1$- International Service Organization
	
	\item Active Minds
	
	\item Young Democratic Socialists
	
	\item Young Americans for Liberty
	
	\item Global Ethical Leadership Society$^1$
	
	\item Residence Hall Association
	
	\item Undergraduate Student Government
	
	\item Ohio Sierra Club$^1$
      \end{enumerate}
      
    \subsection*{Other Groups}
      \begin{enumerate}
      	\item Anime Club$^2$
      	
      	\item Mock Trial$^2$
      	
      	\item Magic Club$^2$
      	
      	\item Rocket Team$^2$
      	
	\item Archery Club$^1$
	
	\item Campus Research Positions
	
	\item ThinkBox$^1$ - a CWRU Entrepreneurial engine
	
	\item CWRU Acts of Random Kindness$^1$
	
	\item Big Games Club$^1$
	
	\item CWRU Fencing$^1$
	
	\item Role Playing Games$^2$
	
	\item Medieval Combat Club
	
	\item Wittke Staff/Faculty Awards Selection Committee
	
	\item Physics and Astronomy Club$^1$
	
	\item Ignite TV
	
	\item Kendo Club
	
	\item Hacker's Society$^1$
	
	\item Food Club
	
	\item La Alianza
	
	\item IFC
	
      \end{enumerate}

  We have a rich variety of involvement, and we encourage our brothers to continue exploring our campus. We look forward to continuing to make an impact at CWRU. The listing above does not encompass the variety of conferences and intiatives that we have been involved with through Greek Life and outside of it. Ultimately, many of our involvements stem from philanthropic and service pursuits that we enjoy.
