\chapter{Community Service and Philanthropy Programming}

  The brothers of Beta Nu engage in a broad variety of service and philanthropy efforts. Service plays an important part of the culture of Theta Chi. It starts at the New Member Education program, where the candidates are required to plan a service or philanthropy event. For example, this semester, the candidates held a Smash Bros tournament, raising over \$200 for the USO. It then continues throughout our time as brothers, whether it counts towards Case Greek Life requirements or not. We believe in serving the communities we are a part of, which is why you can see so many of us work on major volunteer projects during the summers as well the the school year. Service is part of daily life at Theta Chi, with the Service Chair providing service opportunities every chapter meeting for brothers. Recently, our President had his head shaved as part of a raffle meant to encourage brothers to perform more service hours- for every 3 hours of service you complete, you get another raffle ticket.
  
  \section*{By The Numbers}
  In the past year, we have completed 546 hours of officially documented service, a remarkable  59.6\% increase from the 342 where we were last year, and a 76.1\% increase from the 310 the year before. This puts us at 55\% of our service goal for the year, which when you add at least another 150 or so hours being processed, puts us on track to reach 1000 by the end of the semester. We are also already at 205\% of our philanthropy goal of \$1000, with more still to be processed. We are proud of this progress.
  
  \section*{Our Service Pursuits}
   Our service pursuits include but are not limited to the following:
      
    \begin{enumerate}
      \item Summer Grassroots Training: Throughout the summer, a brother helped organize events for the Summer Grassroots Training organization, which aims to educate people about the environment.
      \item The Cincinatti Mayor's Corporate Challenge: During his time on Co-op, a brother helped the city of Cincinatti by working on beautification projects (specifically, planting flowers in gardens).
      \item Sierra Club: Throughout the summer, a brother helped the Sierra Club (an environmental association) by organizing documents and events, as well as teaching others about environmental policies.
      \item Camp Kesem: Throughout the summer, a brother served as a camp counselor for Camp Kesem. The goal of this organization is support children whose parents have developed cancer.
      \item Tutoring at Detroit Metropolitan Schools: During the summer, a brother helped teach Geometry and Pre-Algebra to students at Detroit Metropolitan Schools.
      \item Replay for Kids: In this event, brothers help modify electronic toys so that children with disabilities can still enjoy them. This event has become a staple of our Spring recruitment, often being used as a service event that is accessible to potential new members on campus.
      \item Gray's Armory Museum: After being invited to help by an alum, brothers help restore and repair The Cleveland Gray's Armory and Museum in the heart of Cleveland. This generally results in repainting walls, tearing down dilapidated portions of the building, and restoration.
      \item Graveyard Charge: In the fall, brothers come together to beautify The East Cleveland Township Cemetary. Given that this takes place in the fall, brothers are tasked with raking leaves and reassuring that the cemetary remains clean.
      \item Church of the Covenant Saturday Tutoring: Most Saturdays, a brother would tutor Geometry, alongside other technical subjects, to students at The Church of the Covenant.
      \item Science Olympiad: The Science Olympiad is a competition of sorts, where students from high school and middle school test their knowledge of different aspects of science. Brothers aided the organizers of this event by overseeing the event, as well as being judges.
      \item Cleveland Food Bank: Brothers helped prepare and package food for the less fortunate.
      \item FIRST Robotics: A few brothers volunteered at the FIRST Buckeye Regional Competition. High school students spend six weeks building a robot, learning teamwork and engineering skills to solve complex problems, and then at the end of the build season get to compete at these events.
      \item Habitat for Humanity: Brothers have helped build homes for the less fortunate.
      \item Teach Kids Code: Brothers travel to a local elementary school to teach younger students introductory concepts of coding / programming. This is done through the Java programming language.
      \item Saturday of Service: Once a semester, on a specific date, most brothers sign up for several hours of service. This is known as the Saturday of Service. Generally, most brothers sign up for Kids Against Hunger, where they package prepared meals for the less fortunate.
      \item Lambda Eta Mu Service Honors Society: We have had several brothers initiated into the professional service Fraternity on campus (Lambda Eta Mu). They are tasked with organizing events and attending several different types of service events around the greater-Cleveland area.
      \item United Service Organizations: In the Spring semester of 2016, our candidates organized a Super Smash Brothers tournament to raise funds for the USO. After a large attendance, roughly \$200 was raised.
      \item Magic Tournament Judge: In the Spring semester, brothers judged a charity tournament for Magic: The Gathering.
      \end{enumerate}
      
    \section*{Our Philanthropic Pursuits}
      Our philanthropic pursuits include, but are not limited to, the following:
      
      \begin{enumerate}
      	\item Coordinating/running Mental Health Awareness Week (See Sacred Purpose).      	
      	\item Active Involvement in Relay for Life: We walk in remembrance of cancer victims and raise funds for the American Cancer Society.      	
      	\item NAMI Walks of Greater Cleveland: Walk to raise money for services regarding mental illness in our community. Last summer, a brother helped raise over \$600.
      	\item Our participation in other Greek Fraternity/Sorority philanthropic events, including Mr. CWRU, KATWalk, Anchor Splash, Domestic Violence Awareness Week, and much more.      	
      	\item Participate ``Meatless Mondays`` and other initiatives on environmental and resource conservation.
      \end{enumerate}
      
    \section*{Our Leadership in Service and Philanthropy}
      Our brothers go beyond just serving in service pursuits. They lead in making an impact throughout CWRU and even the USA. We have brothers who, this past year...
      
      \begin{enumerate}      	
      	\item Lead marches on various issues, specifically those on the environment.
      	\item Ran a week long camp serving children whose parents have cancer
      	\item Helped create a survey on mental health at CWRU to reach the entire student body that will lead to mental health policy reforms in the CWRU administration
      	\item Lead service workshops for Replay for Kids for all CWRU students.
      	\item Lead a week long campaign on Mental Health (See Sacred Purpose).
      \end{enumerate}