\chapter{Internal Cooperation}
  The past two semesters, we have seen an increase in Beta Nu’s endeavors to reach out and involve itself with International Headquarters and local chapters. 
  
  \section*{Conferences}
    Among the staple conferences are our chapter endeavors to attend, such as the Deranian’s Presidential Conference and Mid-Year Leadership Conference. Our chapter has sent brothers to several local and international conferences. CWRU's Greek Life Academy program featured a training program for Case Greek Life members; three brothers attended. Meanwhile, our chapter sent both a brother and a candidate to the Catalyst Program, an initiative focused on revealing and solving the sexual assault problem on CWRU's and others' campuses. Another conference we attended was the Culture of Care summit. Finally, in July 2014, our chapter sent two brothers to the 158th Anniversary National Convention, where Beta Nu was awarded Chapter Excellence for the 2013-14 school year. Attached below are the emails corresponding with the Convention activities that affected our chapter. \\
    
    In the future, we plan on sending brothers to more IHQ sponsored conventions. Among the few conventions we will send brothers includes the Initiative Academy and the Mid-Year Leadership Conference. Unfortunately, we could not attend the Spring 2015 MYLC due to perilous driving conditions from Cleveland to Kentucky. \\
    
    As in previous semesters, we will also be hosting Brother Zack Brown, a field executive, later in April this semester. Brother Brown will be performing checklists and surveys of our chapter to help facilitate our growth.  He will also schedule meetings with our Greek Life Advisor, chapter executive board, and he will hold a chapter workshop. We look forward to hosting him and learning tools to help our chapter grow. \\
    
    Finally, we plan on continuing the success of our alumni relations event that involved the international fraternity, OX Roast. We hosted our National Vice President, Joseph Couch, at our OX Roast. In the past, we have hosted the National Secretary, President, and several notable speakers. 
    
  \section*{Local Cooperation}
    Our chapter has made it a point of pride to maintain close relationships with the Beta Lambda chapter of the University of Akron and the Delta Theta chapter of the University of Toledo. We have frequently attended Beta Lambda's initiation, and they have done the same for our initiation. Additionally, we have sent some officer transition documents to Toledo at their request for organizational assistance. \\

    With the assistance of our legal advisor and Beta Nu alum, Daniel Neumann, our chapter will be implementing a chapter specific scholarship fund. The creation of the fund is in part due to the encouragement of IHQ to further the assistance of our brothers’ academics and engage with IHQ. \\

 