\chapter{Social Programming}

  Beta Nu has sought to improve the way it both plans and executes social events this past year through building connections with other campus organizations as well by revamping our documentation process.  Furthermore, we have attempted to foster an improved campus image by encouraging members to join and achieve leadership positions in various campus organizations.
    
  \section*{Greek Week}
    Every year, Beta Nu has a blast participating in CWRU's Greek Week. From the Variety Show, Greek Sing, Pyramid, Rope Pull events among others, we enjoy the opportunity to grow closer as a chapter through the time-consuming yet fun competition. We continue our partnership- known to campus as the Unholy Alliance- with the Zeta Beta Tau Fraternity. Last year, we coordinated with each other's Variety Show, cheered each other on at the competitions, and so far this year have had instruction on how to better perform at Rope Pull. \\
    
    Last year, we won the Spirit Award. We intend on claiming it again, and regaining the tradition where in the past decade, we had a 6 year winning streak on the award.
    
  \section*{Mixers}
    
    We continued building closer relations with other Greeks through a number of new and old mixers. For one of the sororities with which we are very close, Phi Sigma Rho, we had our 15th annual Iron Chef cook-off this Spring. We continued the tradition of sharing Thanksgiving dinner with the sisters of Alpha Phi for approximately its 31st year. \\
    
    This fall, we had a Halloween pumpkin carving with the women of Sigma Psi to promote the Halloween Spirit not only within our two organizations but also with the nearby freshman dorms to whom we invited to carve our extra pumpkins.  Latter in the spring semester we held "Sausage Fest" with Delta Upsilon which we hope to establish and expand as a yearly event.
    
  \section*{Damage}
    For the past 20+ years on the weekend before spring finals, the brothers of Beta Nu have hosted Damage. At this event, we invite the CWRU community to our front yard to blow off steam and smash some cars. We buy two junker cars, have them prepared by a third-party company to be made safe for public destruction, and let the campus have at them with sledgehammers (after signing safety waivers, given instructions, time limits, etc, of course). This event regularly draws hundreds of students as well as many of our alumni to the house, and is an event we are proud to be continuing.
  
  \section*{4th of July BBQ}
    Brothers who stayed in the house for the summer held a 4th of July party, barbecueing in the side yard, bringing out our speakers, inviting a few dozen friends, and watching fireworks shows as night fell.
  
  \section*{Formal}
    Each spring, we hold our formal- this year to the Cleveland Aquarium- taking brothers and their dates. This provides us a way to enjoy ourselves before gearing up for that last string of exams and finals, and gives us an opportunity to get together as a chapter outside of the chapter room and get off campus, eat, and dance.
      
  \section*{Candidate Social Events}
    As part of the new member education program, the candidates are supposed to plan and hold a social event. For the Fall pledge class, they hosted a Murder Mystery Dinner, bringing dozens of guests to the house for a well put together evening of fun and mystery. \\
    
    This semester, the candidates already held an event with a multi-purpose social/service/recruitment event, a Smash Bros Tournament, bringing friends and potential new members to the house where we charged people to participate while getting an opportunity for unaffiliated men to socialize with the brothers. They held an additional event later in the semester- ``Cupcakes and Catan'', which will involve baked goods and board games open to the public.
