\chapter{Introduction Letter}

Dear Theta Chi, \\

We are very proud of our chapter these last two semesters. We have done so much to make our journey more meaningful, and we are recruiting more men who reflect our values. This application will walk you through the rich variety of initiatives we have started, our chapter goals, and it will describe how we have made ourselves and our alma mater better. In addition, this document will feature core information followed by an appendix with all documentation. \\

First and foremost, Beta Nu of Theta Chi has found something to advocate for that will hopefully define our identity for generations to come - Mental Health Awareness (MHA). The sacred purpose initiative has lit a fire inside of our chapter that we never knew existed. Sometimes getting volunteers for something is a struggle, but for MHA week, this was not the case. When we recruit, we are now known for this initiative. University offices, including disability services, and student organizations are reaching out to us and asking to partner with us when we do MHA week next semester. We look forward to facilitating an even bigger MHA week this coming fall. \\

Last semester, through improved documentation and communication, Beta Nu has achieved better officer transitions. We also worked to improve our chapter’s culture of leadership by encouraging those that have concerns or ideas to speak with the relevant officer, rather than immediately approaching the President or Vice President.  Externally, our goals included increasing campus involvement both within and outside of Greek Life, including our first annual Mental Health Awareness Week.  \\

Already this semester the chapter is working to improve alumni engagement, utilize our Chapter Specific Scholarship Fund (CSSF) for brothers in need, improve membership development programs, and continue to improve our scholarship and goal setting initiatives. Already this semester we have had 5 membership development events and many alumni have visited our chapter. Now our alumni attend our meetings in a new rotational system that allows for them to engage with us in a more flexible time schedule. We also plan on awarding multiple scholarships from our CSSF as we raise funds to increase the fund's balance. We have a commitment from our housing corporation to match any funds raised, as well as donate around \$10,000 to the CSSF. One of the final items worthy of note that we have conducted this semester is the \textit{Your Time at Theta Chi} survey. This survey provides a vast amount of valuable information about chapter opinion on topics ranging from service to scholarship, and it will guide us as we continue to work towards improving ourselves and our chapter. \\

This is but a handful of our accomplishments over these last two semesters. There will always be aspects of the chapter that we can strengthen, and we look forward to playing a role in this journey. Beta Nu has never made us prouder, and we know our future looks bright. \\

As one of our favorite alumnus once said, “Be proud, but not satisfied.” While we celebrate our successes, we have to be wary of becoming complacent. There is always room to grow, and we will capitalize on every opportunity available. \\

Sincerely,
Aditya Rengaswamy and Alec Frye
