\chapter{Alumni Programming}

  The Alumni Relations Committee is responsible for the organization and administration of alumni programming and outreach. Its primary tasks include organization of alumni-involved parties, such as the Christmas Party in the Fall Semester and the Founder's Day Party in Spring Semester. It also keeps the alumni database up to date and coordinates news releases with our semester alumni newsletter. Specifically, this is achieved by having alumni sign up for dates to visit our chapter ahead of time on a monthly rotating basis. This has led to a substantial increase in alumni participation in the chapter as a whole thanks to offering more flexible scheduling.

  \section*{OX Roast}
    Over the past year, we have held a number of alumni oriented events with strong alumni participation. The largest of these was our annual OX roast. This year had the best attendance we have ever received, in large part due to the work of our last OX Roast chair, who contacted alumni often and early- not just through the email list, but also by mailing letters to all we had valid addresses for. The event takes place during homecoming where we showcase the chapter accomplishments from the past year with parents, alumni, and a representative from IHQ. This year we had the pleasure of hearing Brother Darnell Parker, board member of the Syracuse chapter, former advisor to the Missouri chapter, and member of the CWRU administration, speak. In addition, during OX roast we held our big brother ceremony and the OX memorial ceremony. Both of these ceremonies allow us to share more public traditions with our significant others, alumnus brothers, and friends.
    
  \section*{Other Alumni Events}
    We also held a number of smaller events. We continued our annual celebration of the Christmas season with a joint Christmas party. The house is decorated in the style of holiday spirit, with a festive tree and a Secret Santa Exchange. \\
    
    We celebrate our Founder’s Day every year with a sit down dinner with our alumni. Beginning last year, we found a manuscript of a radio play describing the first chapter meeting with Frederick Norton Freeman and Arthur Chase. We performed it in a manner that made it feel like a traditional radio drama, and we intend to continue it this year and in future years.
    
    This spring, we also held an Alumni/Active Social, where we had a game/poker night as well as dinner at The Jolly Scholar.
    
  \section*{Alumni Communication}
    The main method of communication between the active chapter and alumni is our alumni email list. This keeps alumni informed of all chapter events. The list contains roughly half of the chapter’s alumni, and we use it communicate with our alumni, and the alumni use it to communicate with each other. \\

    Over the past year, alumni have shared some amazing news, including the introduction of several adorable children, and shared with the actives some fantastic advice on how to get a job. The chapter also publishes a yearly newsletter, maintains a website, and Facebook page. These are used to publish news of upcoming events.
    
  \section*{Alumni Board}
    Our chapter advisors serve as an integral part of our chapter having been established last year. As officers are:
      \begin{enumerate}
       \item Chapter Advisor - Daniel Neumann
       \item Vice President Advisor - Dan Okienko
       \item Health and Safety Advisor - JJ Moffitt
       \item Secretary Advisor - Aditya Rengaswamy
	   \item Financial Advisor - John Boyer
       \item Member Education Advisor - Dan Snow
       \item Recruitment Advisor - Matt Richter
       \item Faculty and Scholarship Advisor - Rich Drushel
       \item Member-at-Large - Walt Mahovlich
       
      \end{enumerate}

   Attached are bylaws for the Alumni Board. For the Beta Nu Housing Corporation, alumnus Robert Divincenzo serves as President, meeting with the House Manager regularly and ensures the chapter house stays in working order and works with the University. Additionally, we have a Legal Advisor, alumnus Dan Myers. 
    
  \section*{Alumni Engagement}
    Our alumni have been extremely active in our ritual ceremonies, with quite a few showing up to both the public and private events and initiation ceremonies. In addition to alumni attending our Initiations, alumni ceremonies, and other public ceremonies, we have had alumni actively attend and participate in our Candidate Education Program and Member Development Program. Our alumni have provided excellent advice on topics such as personal finance, tax filing, and creating resumes. Our alumni also provide sound advice, assistance and service in other aspects of chapter operations. For example, Brother Daniel Neumann assists with the operation of the chapter web site and Brother Moffitt has helped Beta Nu engage with a variety of initiatives that Greek life as a whole has adopted.  \\

    Our alumni are integral to our success, and we make every effort to recognize them. New initiatives we plan on starting include sending them hand written thank you cards each summer. Their efforts have helped us thrive and we look forward to many more years with them by our side.