\chapter{Community Service and Philanthropy Programming}

  The brothers of Beta Nu engage in a broad variety of service and philanthropy efforts. Service plays an important part of the culture of Theta Chi. It starts at the New Member Education program, where the candidates are required to plan a service or philanthropy event. It then continues throughout our time as brothers, whether it counts towards Case Greek Life requirements or not. We believe in serving the communities we are a part of, which is why you can see so many of us work on major volunteer projects during the summers as well the the school year. Service is part of daily life at Theta Chi, with the Service Chair providing service opportunities every chapter meeting for brothers. Recently, we have implemented a service leadership plan, which will be included in the additional documentation.
  
  \section*{By The Numbers}
  In the past year, we have completed 1007.0 hours of officially documented service, a remarkable  57.9\% increase from the 637.5 where we were last year, and a 194.4\% increase from the 342 the year before. This puts us at 116.4\% of our service goal for the year, which when you add an estimated 100 or so hours being processed, puts us on track to clear our Greek Life Office expectation with ease. We are also already at 210\% of our philanthropy goal of \$1,000, with \$2,100. We are proud of this progress.
  
  \section*{Our Service Pursuits}
   Our service pursuits include but are not limited to the following:
      
    \begin{enumerate}
      \item Sierra Club: Throughout the summer, a brother helped the Sierra Club (an environmental association) by organizing documents and events, as well as teaching others about environmental policies.
      \item Camp Kesem: Throughout the summer, a brother served as a camp counselor for Camp Kesem. The goal of this organization is support children whose parents have developed cancer.
      \item Replay for Kids: In this event, brothers help modify electronic toys so that children with disabilities can still enjoy them. This event has become a staple of our Spring recruitment, often being used as a service event that is accessible to potential new members on campus.
      \item Gray's Armory Museum: After being invited to help by an alum, brothers help restore and repair The Cleveland Gray's Armory and Museum in the heart of Cleveland. This generally results in repainting walls, tearing down dilapidated portions of the building, and restoration.
      \item Graveyard Charge: In the fall, brothers come together to beautify The East Cleveland Township Cemetary. Given that this takes place in the fall, brothers are tasked with raking leaves and reassuring that the cemetary remains clean. Additionally, this will be happening again in in the spring after the application to beautify the cemetary before the summer season.
      \item Church of the Covenant Saturday Tutoring: Most Saturdays, a brother would tutor Geometry, alongside other technical subjects, to students at The Church of the Covenant.
      \item Science Olympiad: The Science Olympiad is a competition of sorts, where students from high school and middle school test their knowledge of different aspects of science. Brothers aided the organizers of this event by overseeing the event, as well as being judges.
      \item Cleveland Food Bank: Brothers helped prepare and package food for the less fortunate.
      \item FIRST Robotics: A few brothers volunteered at the FIRST Buckeye Regional Competition. High school students spend six weeks building a robot, learning teamwork and engineering skills to solve complex problems, and then at the end of the build season get to compete at these events.
      \item Vex Robotics Scholastic Competition: A few brothers volunteered at the Vex Robotics Competition. High school students build a robot, learning teamwork and engineering skills to solve complex problems, and then at the end of the build season get to compete at these events.
      \item Teach Kids Code: Brothers travel to a local elementary school to teach younger students introductory concepts of coding / programming. This is done through the Java programming language.
      \item Saturday of Service: Once a semester, on a specific date, most brothers sign up for several hours of service. This is known as the Saturday of Service. Generally, most brothers sign up for Kids Against Hunger, where they package prepared meals for the less fortunate.
      \item Kids Against Hunger Cleveland: After founding the organization, one brother is now the advisor, helping them serve over 300,000 meals to those in Cleveland and an additional 20,000 around the world.
      \item MedWish: a not-for-profit organization that saves lives and the environment by repurposing discarded medical supplies and equipment to provide humanitarian aid in developing countries. 
      \item NextGen Climate Change: acts politically to prevent climate disaster and promote prosperity for every American. 
      \item Cleveland Environmental Action Network: works to benefit the environmental advocates in the Greater Cleveland area.
      \item Alpha Phi Omega: is a national coeducational service organization founded on the principles of Leadership, Friendship and Service.
      
      \end{enumerate}
      
    \section*{Our Philanthropic Pursuits}
      Our philanthropic pursuits include, but are not limited to, the following:
      
      \begin{enumerate}
      	\item Coordinating/running Mental Health Awareness Week (See Sacred Purpose).      	
      	\item Active Involvement in Relay for Life: We walk in remembrance of cancer victims and raise funds for the American Cancer Society.
      	\item Marfan Foundation: We have donated to them through supporting Alpha Phi Omega.
      	\item The V Foundation: Supporting it by helping out Delta Chi's on campus
      	\item Our participation in other Greek Fraternity/Sorority philanthropic events, including Mr. CWRU, KATWalk, Anchor Splash, Dash for Domestic Violence Awareness, and much more.
      \end{enumerate}
      
    \section*{Our Leadership in Service and Philanthropy}
      Our brothers go beyond just serving in service pursuits. They lead in making an impact throughout CWRU and even the USA. We have brothers who, this past year...
      
      \begin{enumerate}
	\item Discussed and engaged with complexities in topics ranging from the environment to corporate finance, serving as VP of finance managing budgets, participating in a variety of events put on by the Global Ethical Leaders Society, working closely with the Inamori Center for Ethics and Excellence at CWRU.
      	\item Attended a summit of youth organizations going to the United Nations Framework Convention on Climate Change to help those who were going to the conference work on their policy
      	\item Ran a week long camp serving children whose parents have cancer
      	\item Coordinated the CCEL Scholars Program, the Center from Civil Engagement and Learning
      	\item Helped create a survey on mental health at CWRU to reach the entire student body that will lead to mental health policy reforms in the CWRU administration
      	\item Lead service workshops for Replay for Kids for all CWRU students.
      	\item Lead a week long campaign on Mental Health (See Sacred Purpose).
      \end{enumerate}