\chapter{Internal Cooperation}
  The past two semesters, we have seen an increase in Beta Nu’s endeavors to reach out and involve itself with International Headquarters and local chapters. 
  
  \section*{Conferences}
  
    Among the staple conferences are our chapter endeavors to attend, such as the Sasser's Presidential Conference and Theta Chi University. Our chapter has sent brothers to several local and international conferences. Our chapter president, David Lance, attended Sasser's while our whole EC made it to this year's Theta Chi University at The Ohio State University. CWRU's fall semester Greek Life Academy program featured a training program for Case Greek Life members; two brothers attended- Robert Park and Chris Brace. Meanwhile, our chapter will be sending several brothers to Theta Chi's Initiative Academy. We value the leadership development opportunities these conferences can provide, as many of those who attended are now elected officers for the chapter. \\
    
    We looked forward to hosting a field exec, but was never reach out to by one and was sadly unable to reap those benefits.\\
    
    Finally, we plan on continuing the success of our alumni relations event that involved the international fraternity, $\Theta$X Roast. We hosted Tait Martin, current International Vice President at our $\Theta$X Roast. In the past, we have hosted the Secretary, President, and several notable speakers. 
    
  \section*{Local Cooperation}
    Our chapter has made it a point of pride to maintain close relationships with the Beta Lambda chapter of the University of Akron and the Delta Theta chapter of the University of Toledo. In the past, we have frequently attended Beta Lambda's initiation, and they have done the same for our initiation. With their chapter's rebooting, we made ourselves available to them, attending one of their philanthropy events in support of the new brothers. We have been heavily involved in the recolonization of the Youngstown State Chapter as one of our brothers transfered their, Mark Reinke.\\
    
    With the assistance of our chapter advisor Daniel Neumann, Beta Nu has finally built up enough money in the Chapter-Specific Scholarship Fund that we were able to award one \$500 scholarships this year.

 