\chapter{Introduction Letter}

Dear Howard R. Alter Jr. Award Selection Committee, \\

In the Fall of 2016 and the Spring of 2017, Beta Nu has continued its upward trend started in the previous two years. We, as a chapter, have worked to make the time of our undergraduate members as meaningful and as fulfilling as possible.  The brothers of Beta Nu have recruited men who share our values and will one day lead our chapter. This application will walk you through the accomplishments of our chapter, the effort we have made to improve our alma mater and continued love we share for each other. In addition, any auxiliary information required will be included in the appendix. \\

The Beta Nu chapter hosted the third annual Mental Health Awareness (MHA) Week, which has become a main stay of the chapter and has become an identifying event for the chapter. Leveraging the overwhelmingly positive campus response from last semester, we raised over two thousand dollars for the National Alliance for Mental Illness (NAMI), more than double what we raised last year. Additionally, the awareness created by our programming has directly facilitated the founding of a local NAMI chapter on campus as well as peer to peer care programs in other Greek Organizations. As you will read, the brothers of the Beta Nu have done our best to embody the principles of our Sacred Purpose both within our chapter and throughout our alma mater as a whole. \\

Compared to the previous few semesters, the academic achievements of Beta Nu have greatly improved. Our GPA has been steadily around 3.1 for last few semesters, and we are happy to report for the Fall of 2016, our GPA was 3.268, which is .021 less than last Fall, which points to a stabalized, largely due to focus on improving our internal scholarship programming. While slightly below the all men’s average on campus of a 3.34, we are happy to see improvement and we hope to continue to improve in the coming semesters. \\

Perhaps what we are most proud of this academic year is the formation of Chapter Advisory Board (CAB). Spearheaded by former chapter president and Colley Award winner Daniel Neumann, Beta Nu has a fully staffed CAB with an adviser for each executive position. We are happy to say that each adviser is a local alumnus, all together representing over 40 years of our chapter’s history. \\

Overall, the last two semesters have been successful ones for our chapter. While we may not fully meet every pillar of the Alter Award, we are excited to share our accomplishments with you and look for points of improvement. \\

Love and Respect, \\
David Lance \hfill Jackson Kishbaugh-Maish \\ 
President, BN of $\Theta$X \hfill Secretary, BN of $\Theta$X \\
