\chapter{Scholarship Programming}

	Our chapter is committed to bringing excellence in scholarship. Our fraternity’s motto of ``Alma Mater first, and Theta Chi for Alma Mater'' is a testament towards the devotion we have for our studies. Our scholarship program sets high goals and challenging standards. Beta Nu lives by a motto of proud but not satisfied- we are always trying to improve ourselves as men and scholars. In Fall 2014, our average GPA was a 3.07. Through our scholarship programs and personal efforts, our Fall 2016 GPA was a 3.268. Our goal for next semester, Fall 2017 will be to exceed the All-Mens average, which is about a 3.30, and then to exceed other benchmarks, like the All-Undergraduates and All-Greek GPAs, which are at about 3.34 and 3.42 respectively.\\

This has led to a variety of efforts to promote high achieving academics including: setting personal and chapter goals at the semester retreat, announcing the number of classes missed during roll call at chapter, creating individualized grade improvement plans, and creating scholarships for brothers, as well as potential new members.\\

In the past, the house was not a productive place to work; it was loud, with no place to study without people socializing around you. To remedy this, signs are posted throughout the house reminding brothers to keep good on their studies. We have a dedicated study room, hold study tables, and enforce quiet hours. \\
  
  \section*{Scholarship Plans and Contracts}
    Each semester, the Scholarship Chair drafts a scholarship plan detailing the academic goals and responsibilities of the chapters members. We have attached the scholarship plan from Fall 2014 as a sample. For those brothers whose GPA falls under a 3.0, and those who desire mentored help, the Scholarship Chair drafts a contract detailing the requirements a brother must perform in order to maintain good standing with the chapter. Specifically, brothers under a 3.0 are required to adhere to the contract lest consequential action be taken.\\

These contracts are typically made in the first week of the semester, with the scholarship chair meeting with the brother in question. They then discuss what happened the previous semester, what were the root causes of academic issues, and from there draw up an individualized contract to help them improve.\\

Current projects include legislation that will require scholarship contracts for all candidates, regardless of their prior semester performance. We want to promote the idea that Beta Nu is an organization that cares about scholarship from the start, and ensure that the people we are bringing into the fraternity have the skills and ability necessary to succeed in their academic affairs.  
    
  \section*{Study Tables}
    Each weekday between 6:30-8:30pm, we enforce quiet hours around the study room in the house. This space is hosted by one of the members of the scholarship committee, and it helps change the environment of this part of the house from a social place to one where brothers and friends can work and focus. Depending on a brother’s scholarship contract, they may be required to attend a certain number of hours of these a week in addition to other requirements.\\

	Additionally, during Finals Week, the house is in continual quiet hours. On one of the reading days, the scholarship chair hosts a study party, where if you study for a prescribed amount of time, he takes you out on a free dinner.
    
  \section*{Study Rooms and Quiet Hours}
   	In addition to the regularly scheduled hours for study tables in the living room, we have dedicated a room to be a 24/7 individual study place. The room is kept clean, and noise level must always remain low. If brothers have a group assignment, a second room, the so-called War Room, is then commandeered as a study space. Additionally, if the study room becomes full, the War Room also becomes a study room with the same enforced rules. The house as a whole also has quiet hours. On weeknights- that is, Sunday through Thursday, the house goes into quiet hours from 11pm-8am. During that time, no one is to be playing loud music, and volume is to be kept to a minimum.
    
  \section*{Scholarship Banquets}
    Scholarship programming is not solely about rules, requirements, or focusing on the negatives. We also like to celebrate high achievement. To do this, every semester we host a banquet, inviting professors to either our house or a campus ballroom. At these banquets, we give recognition to our brothers who have excelled and improved scholastically. We invite professors and faculty who have made an impact on our academic journey. Typically, our Fall banquet is held with another organization as we believe it is important to help other greek chapters to succeed academically. For Fall 2016’s banquet, we co-hosted the event with the sisters of Pi Beta Phi.

  \section*{Professor Meals}
	This year, our scholarship chair, Ryan Hawtof, has continued with a newer program where we can develop relationships with our professors and engage them more. Once or twice per semester, we will invite a professor to the house where we sit down with them for a meal and have a discussion. These events have been well received, and we are excited to continue the program in the future. The event planned for this semester was with a Professor from our school’s Chemistry department who participates in large amounts of research on campus.
    
  \section*{Resolute Man Scholarship}
    At the end of the summer/beginning of each academic year, an email is sent out to the new freshmen informing them of scholarship opportunities. We are proud to bestow the largest fraternity scholarship- \$1000, to any unaffiliated undergraduate male. They fill out an application, come to the house for an interview with the scholarship chair and chapter president, and then attend a educational session during rush that celebrates scholarship and other achievements. We view it as a tool to demonstrate and promote our values while giving us an opportunity to meet stellar students who could be potential new members.
    
  \section*{Scholarship Endownment}  
    This year we are working on developing our endowed Chapter Specific Scholarship fund for brothers. Through the Foundation Chapter’s fund, we were able to award one \$500 scholarships, and we look forward to engaging with alumni to grow this fund. Scholarships are awarded based on contributions to the chapter/and or university, academic performance, and financial need. A committee of BN alumni will select the recipients, who are awarded the scholarship on Founder’s Day.
        
  \section*{Scholarship and Suspension Roundtables}
    Scholarship and Suspension roundtables are designed as a forum for brothers to discuss the standards which we abide by as they relate to scholarship. These standards include cumulative GPA, prior semester GPA, chapter involvement while struggling with academics, and how much information we should gather from struggling brothers. Grades are a sensitive issue and our goal is to pulse the chapter and understand the standards we want to hold each other by. When standards are not met, we discuss the process and procedures for suspending brothers. We want to be cognizant of external issues that contribute to difficulties in scholarship, but not at the expense of maintaining an academic culture. These roundtables have even led to proposals of new legislation in the recent semesters.
