\chapter{Social Programming}

  Beta Nu has sought to improve the way it both plans and executes social events
  this past year through building connections with other campus organizations as
  well by revamping our documentation process.  Furthermore, we have attempted
  to foster an improved campus image by encouraging members to join and achieve
  leadership positions in various campus organizations.
    
  \section*{Greek Week}
    Every year, Beta Nu has a blast participating in CWRU's Greek Week. From the
    Variety Show, Greek Sing, Pyramid, Rope Pull events among others, we enjoy
    the opportunity to grow closer as a chapter through the time-consuming yet
    fun competition. We continue our partnership- known to campus as the Unholy
    Alliance- with the Zeta Beta Tau Fraternity. Last year, we coordinated with
    each other's Variety Show, cheered each other on at the competitions, and so
    far this year have had instruction on how to better perform at Rope Pull.
    Additionally, this year we coordinated our t-shirt designs, and made an 
    "Unoly Alliance" flag to bring to events. \\
    
  \section*{Mixers}
    
    We continued building closer relations with other Greeks through a number of
    new and old mixers. For one of the sororities with which we are very close,
    Phi Sigma Rho, we had our 16th annual Iron Chef cook-off this Spring. We
    continued the tradition of sharing Thanksgiving dinner with the sisters of
    Alpha Phi for approximately its 32nd year. \\

	In the Fall semester we had a movie night with Sigma Psi. Where they came over 
	to watch a movie in our theater room with food as a welcome back to campus event. \\

    Another mixer held in the Spring semester was with Sigma Psi a local sorority 
    chapter at Case Western Reserve. We had them over for a joint Murder Mystery 
    event with dinner and socializing. This was a play on our event last semester, 
    mentioned below. \\
    
    Finally, before the end of the semester we will be having a Trivia night mixer 
    Sigma Sigma Sigma at an undecided location with one of our brothers and one of 
    their sisters coming up with the questions.
    
  \section*{Damage}
    For the past 20+ years on the weekend before spring finals, the brothers of
    Beta Nu have hosted Damage. At this event, we invite the CWRU community to
    our front yard to blow off steam and smash some cars. We buy two junker
    cars, have them prepared by a third-party company to be made safe for public
    destruction, and let the campus have at them with sledgehammers (after
    signing safety waivers, given instructions, time limits, etc, of course).
    This event regularly draws hundreds of students as well as many of our
    alumni to the house, and is an event we are proud to be continuing. \\
  
  \section*{4th of July BBQ}
    Brothers who stayed in the house for the summer held a 4th of July party,
    barbecueing in the side yard, bringing out our speakers, inviting a few
    dozen friends, and watching fireworks shows as night fell. \\
  
  \section*{Formal}
    Each spring, we hold our formal- this year to the Cleveland Museum of Art-
    taking brothers and their dates. This provides us a way to enjoy ourselves
    before gearing up for that last string of exams and finals, and gives us an
    opportunity to get together as a chapter outside of the chapter room and get
    off campus, eat, and dance. \\
      
  \section*{Candidate Social Events}
    As part of the new member education program, the candidates are supposed to
    plan and hold a social event. For the Fall pledge class, they hosted a
    "Cupcakes and Catan" event, where brothers, candidates, and friends got
    together in the house to eat cupcakes and play board games. \\
    
  \section*{Murder Mystery Party}
    For the second year in a row, brothers planned a Murder Mystery party. This
    event continues to be a success, bringing people from other greek
    organizations and the campus as a whole together to solve a mystery, which
    is acted out by brothers. \\

