\chapter{Community Service and Philanthropy Programming}

  \section*{A Look At The Numbers}
    The brothers of the Beta Nu chapter engage in numerous community service endeavors. The past academic year, we completed 342 officially documented Service Hours, a 10\% increase from last year at this time (310 hours). The Greek Life Office at CWRU requires us to have approximately 13 hours of service per year, per member. In the appendices, it shows that as of February, 2015, we are at 65\% of our service goal and 115\% of our \$890 philanthropy goal. These goals are for the end of this school year on May, 2015. \\
    
    In addition to these hours, we currently have at least service 100 hours still being processed by the Greek Life Office. As per the \textit{Your Time at Theta Chi} survey, our chapter goal is to hit at least 100\% of our service hours. Our stretch goal is 120\%, or approximately 650 hours. Our chapter philanthropy goal is 150\%, \$1450. Our stretch goal is 200\%, or \$1800. With current trajectories, we feel confident that we can hit our goals by the end of the year. 
    
    \section*{Our Service Pursuits}
      Our service pursuits include but are not limited to the following:
      
      \begin{enumerate}
      	\item Hats for Heads: Crocheting hats for children at Rainbow Babies suffering cancer and other illnesses.
      	
      	\item People Climate March: Volunteer and brothers lead March logistics in Washington DC for climate change awareness.
      	
      	\item Replay for Kids: Adapt toys to be playable by kids with various disabilities.
      	
      	\item CGP Cleanup: Clean and prepare an urban greenhouse for fruit/vegetable growth.
      	
      	\item Kids Against Hunger: Packed 40,000+ meals for the Cincinnati and Cleveland areas.
      	
      	\item Church of the Covenant Tutoring: Tutor elementary, middle, and high school students in Mathematics, English, ACT prep, and other subjects.
      	
      	\item Volunteering at Rainbow Babies: Some of our brothers give their time to take care of children at the hospital.
      	
      	\item Continued engagement with Lambda Eta Mu, the service honors society at CWRU.
      	
      	\item Beta Nu partnered with affiliates of the USO to provide 100+ encouraging letters and paracord bracelets for active duty military soldiers. People throughout the Greek and non-Greek community contributed!
      \end{enumerate}
      
    \section*{Our Philanthropic Pursuits}
      Our philanthropic pursuits include, but are not limited to, the following:
      
      \begin{enumerate}
      	\item Coordinating/running Mental Health Awareness Week (See Sacred Purpose).
      	
      	\item Active Involvement in Relay for Life: We walk in remembrance of cancer victims and raise funds for the American Cancer Society.
      	
      	\item Our participation in other Greek Fraternity/Sorority philanthropic events, including Mr. CWRU, KATWalk, Anchor Splash, Domestic Violence Awareness Week, and much more.
      	
      	\item Attended/coordinated the People's Climate March in Washington D.C.
      	
      	\item Participate ``Meatless Mondays`` and other initiatives on environmental and resource conservation.
      	
      	\item Civic Engagement Conference: A conference for servant leaders to learn about issues impacting Cleveland and the world.
      	
      	\item What You Do Matters Summit: A summit on stopping hate speech.
      	
      	\item Center for Civic Engagement and Learning(CCEL): Implement programs with this office.
      	
      \end{enumerate}
      
    \section*{Our Leadership in Service and Philanthropy}
      Our brothers go beyond just serving in service pursuits. They lead in making an impact throughout CWRU and even the USA.
      
      We have brothers who, this past year...
      
      \begin{enumerate}
      	\item Lead/advise non-profits like Kids Against Hunger that they founded.
      	
      	\item Lead marches on various issues, specifically those on the environment.
      	
      	\item Lead all logistics for the Civic Engagement Conference, an event with 200+ attendees who engaged in various break-out sessions and group work over Greater Cleveland community involvement.
      	
      	\item Lead programs and coordinated  \textit{What You Do Matters}, a summit on putting a stop to hate speech done in collaboration with the United States Holocaust Memorial Museum.
      	
      	\item Lead service workshops for Replay for Kids for all CWRU students.
      	
      	\item Served as a CCEL Student Executive council member to help plan and run Civic Engagement events.
      	
      	\item Lead a week long campaign on Mental Health (See Sacred Purpose).
      \end{enumerate}
      
      We take pride in what our brothers continue to accomplish all over this University and beyond its borders. This is but a sample of the impact we have made on our community - an embodiment of 'the Assisting Hand'.

    \section*{Understanding the Why}
      As per the \textit{Your Time at Theta Chi} survey, we have gotten critical feedback and reflection on the efforts people have spent participating in service and philanthropy events. Brothers have shared heartfelt experiences of the struggles their families have faced with cancer, disabilities, and mental health. These stories help us create meaning out of what we do. Our conversational reflections on service have helped us find new venues to serve as well. When people speak about their passions, we get a chance to either create or grow opportunities within our campus that are working to make a change. Understanding the why of who we are has been a greater focus these last two semesters, and that has helped us in all aspects of our brotherhood.
