\chapter{Scholarship Programming}
%\noindent

  Our chapter is committed to bringing excellence in scholarship. Our fraternity's motto of ``Alma Mater first, and Theta Chi for Alma Mater'' is a testament towards the devotion we have for our studies. Our scholarship program sets high goals and challenging standards. In light of the difficult period our chapter has faced with regards to scholarship, we have revised our programs and worked towards creating better study environments in order to assist struggling brothers and candidates. \\ 

  This has led to a variety of efforts to promote high achieving academics including: setting personal and chapter goals at the semester retreat, announcing the number of classes missed during roll call at chapter, creating individualized grade improvement plans, and creating scholarships for brothers, as well as potential new members. \\

  In the past, the house was not a productive place to work; it was loud, with no place to study without people socializing around you. To remedy this, signs are posted throughout the house reminding brothers to keep good on their studies and that the ``scholarship chair is watching''. We have a dedicated study room, regularly hold study tables, and enforce quiet hours.
  
  \section*{Scholarship Plans and Contracts}
    Each semester, the Scholarship Chair drafts a scholarship plan detailing the academic goals and responsibilities of the chapters members. We have attached the scholarship plan from Fall 2014 as a sample. For those brothers whose GPA falls under a 3.0, and those who desire mentored help, the Scholarship Chair drafts a contract detailing the requirements a brother must perform in order to maintain good standing with the chapter. Specifically, brothers under a 3.0 are required to adhere to the contract lest consequential action be taken. \\

    These contracts are typically made in the first week of the semester, with the scholarship chair meeting with the brother in question. They then discuss what happened the previous semester, what were the root causes of academic issues, and from there draw up an individualized contract to help them improve. \\

    Current projects include legislation that will require scholarship contracts for all candidates, regardless of their prior semester performance. We want to promote the idea that Beta Nu is an organization that cares about scholarship from the start, and ensure that the people we are bringing into the fraternity have the skills and ability necessary to succeed in their academic affairs.
    
  \section*{Chapter and Personal Goals}
    During this past retreat, the brothers were given the \textit{Your Time at Theta Chi} survey, which included questions regarding their scholarship goals. In comparison to the 3.07 average GPA the chapter last received, our members have a personal average goal of reaching 3.41. As a chapter, we feel that our GPA together should be at least 3.375. This shows, once again, our theme of being proud but not satisfied.
    
  \section*{Study Tables}
    Each weekday between 6:30-9:00pm, we turn the living room into a quiet study space. This space is hosted by one of the members of the scholarship committee, and it helps change the environment of the house from a social place to one where brothers and friends can work and focus. Depending on a brother's scholarship contract, they may be required to attend a certain number of hours of these a week in addition to other requirements. 
    
  \section*{Study Rooms and Quiet Hours}
    In addition to the regularly scheduled hours for study tables in the living room, we have dedicated a room to be a 24/7 study place. The room is kept clean, and noise level must always remain low. If brothers have a group assignment, a second room, the so-called “War Room,” is then commandeered as a study space. Additionally, if the study room becomes full, the War Room also becomes a study room with the same enforced rules.  The house as a whole also has quiet hours. On weeknights- that is, Sunday through Thursday, the house goes into quiet hours from 10pm-8am. During that time, no one is to be playing loud music, and volume is to be kept to a minimum.
    
  \section*{Scholarship Banquets}
    Scholarship programming is not solely about rules, requirements, or focusing on the negatives. We also like to celebrate high achievement. To do this, every fall we co-host a banquet at one of campus ballrooms along with one of the sororities. This year, we held it with the women of Phi Sigma Rho. At these banquets, we give recognition to our brothers and their sisters who have excelled and improved scholastically. We invite professors and faculty who have made an impact on our academic journey. We also have speakers from Case's ESS- Educational Services for Students- give a presentation on something scholarship related. \\

    In the spring, we hold a similar type of dinner, but keep it simpler and in the house.
    
  \section*{Resolute Man Scholarship}
    At the end of the summer/beginning of each academic year, an email is sent out to the new freshmen informing them of scholarship opportunities. We are proud to bestow the largest fraternity scholarship- \$1000, to any unaffiliated undergraduate male. They fill out an application, come to the house for an interview with the scholarship chair and chapter president, and then attend a educational session during rush that celebrates scholarship and other achievements. We view it as a tool to demonstrate and promote our values while giving us an opportunity to meet stellar students who could be potential new members.
    
  \section*{Scholarship Endowment}
  
    This year we are working on developing our endowed Chapter Specific Scholarship fund for brothers. Through the Foundation Chapter's fund, we have currently raised \$14,095. We will be awarding \$700 in scholarships next semester, and we look forward to engaging with alumni to grow this fund. The details of our plan are included in an email in the appendices.  Over the next year, we have a guaranteed \$10,000 gift to the fund, and the chapter's Housing Corp. has promised to match any additional funds we can raise. We are excited by these prospects and will be pleased to see the results it can bring to help the brothers of Beta Nu.
    
  \section*{Notes Bank}
    In the past, scholarship chairs have attempted to create a system in which brothers can share past resources from classes they have taken. However, these initiatives were never very well organized and thought through, so after a semester or a year, each would die out. \\

    This semester, our notes initiative makes use of pre-existing chapter information channels. This will allow the bank to be easily accessible to all brothers. Additionally, the work required of future scholarship chairs in maintaining it will be lower. Finally, since it is entirely electronic, the chance of losing older materials is negligible. To ensure that this new resource is utilized, any brother who contributes to it each semester is placed into a \$200 raffle.
    
  \section*{Scholarship and Suspension Roundtables}
    Scholarship and Suspension roundtables are designed as a forum for brothers to discuss the standards which we abide by as they relate to scholarship. These standards include cumulative GPA, prior semester GPA, chapter involvement while struggling with academics, and how much information we should gather from struggling brothers. Grades are a sensitive issue and our goal is to pulse the chapter  and understand the standards we want to hold each other by. When standards are not met, we discuss the process and procedures for suspending brothers. This past roundtable brought further clarity to what we want out of the suspension process. We want to be cognizant of extneral issues that contribute to difficulties in scholarship, but not at the expense of maintaining an academic culture.