\chapter{Social Programming}

  This year, Beta Nu has stepped up its efforts to provide varied social programming, and increase its involvement as an organization on campus by starting up new events, maintaining annual traditions, and revitalizing older traditions.
  
  \section*{Greek Week}
    
    The chapter had a blast participating in the ``90's themed'' Greek Week at Case Western Reserve. We gave a well received comedic performance during the Greek Sing competition, leaving the audience laughing and applauding. We placed highly in the pyramid competition, where instead of aiming solely for time as the criteria required, we decided to build a full extension five row pyramid. We also, for the first time in at least five years, won a rope pull match. \\

    We revitalized a partnership known as the ``Unholy Alliance'' between ourselves and Zeta Beta Tau. We cheered each other on during the festivities, and also coordinated our Variety Show performances. \\

    Because of the effort and attitude we gave Greek Week this year, it culminated in the chapter winning the Spirit Award.
    
  \section*{Mixers}
    
    We continued building closer relations with other Greeks through a number of new and old mixers. For one of the sororities with which we are very close, Phi Sigma Rho, we had our 14th annual Iron Chef cook-off this Spring. We continued the tradition of sharing Thanksgiving dinner with the sorority Alpha Phi for approximately its 30th year. We continued our annual shared scholarship dinner this year with Phi Sigma Rho. \\

    We also tried some new mixers, which included carving pumpkins with Phi Sigma Rho, holding an improv games night with Delta Upsilon, and inviting the women of Alpha Chi Omega to our home for a multicultural potluck dinner. \\

    As part of our new member education program, the candidates put on a social event of their own. This fall, that meant inviting the brothers of the Beta Lambda chapter of Theta Chi from Akron to come over for a movie and brotherhood meal. Unfortunately, they had to back out at the last minute due to unforeseen circumstance, but our brothers still watched Citizen Kane together and enjoyed curry. This spring, the candidates have planned a game night at the house, which will be open to the public.
    
  \section*{Athletics}
    
    Brother Mcginnity wated our chapter to be more involved with interfraternal and campus athletics. This year, we participated in intramural football and soccer, which led to Theta Chi playing in the soccer playoffs. We are looking forward to playing in these seasons next year, where hopefully we can come out with a trophy. Additionally, as part of our Mental Health Awareness Week, we hosted a Ultimate Frisbee tournament to the campus community. Lastly, we also put together teams to participate in others' tournaments. We played in Alpha Chi Omega's dodgeball tournament, swimming in Delta Gamma’s Anchor Splash, as well as playing in the Case Quidditch Team's quidditch tournament.
    
  \section*{Damage}
  
    For the past 20+ years on the weekend before spring finals, the brothers of Beta Nu have hosted Damage. At this event, we invite the entire CWRU community to our front yard to blow off steam and smash some cars. We buy two junker cars, have them prepared by a third-party company to be made safe for public destruction, and let the campus have at them with sledgehammers (after signing safety waivers, given instructions, time limits, etc, of course). This event regularly draws several hundred people to our house, and is an event we are proud to be continuing.
    
  \section*{Formal}
  
    Each spring, we hold our formal where we go to the Cleveland Metroparks Zoo taking brothers and their dates. This provides us a way to enjoy ourselves before gearing up for that last string of exams and finals, and gives us an opportunity to get together as a chapter outside of the chapter room and get off campus, eat, and dance.
    
  \section*{Humans vs. Zombies}
     
    Every semester, the Big Games Club puts on a ten day long campus wide game of Humans vs. Zombies (HvZ). As a geeky school, this is a major event and campus tradition. Beta Nu takes this game very seriously. Aside from having a large portion of the club leadership coming from our brothers, as well as having an appointed position ``Zombie Defense Chair``, our Social Closet is colloquially called ''The Armory.'' The closet has a plethora of Nerf guns stored inside for use during this week. Each semester, the chapter forms one or two teams to compete, and is always in the top five teams.
    
  \section*{Brotherhood Events}
    
    During chapter, the Chaplain opens the floor to brotherhood events coming up during the week. Often, these will be things like curry nights, movies, theater shows, etc. However, there are a few regularly programmed events:
    
    \subsection*{Chaplain's Chowdowns}
      Occasionally, there is a topic of interest we feel that the chapter needs to work through and discuss, but trying to squeeze it into a chapter meeting doesn’t feel appropriate. The chaplain then will schedule and host a chowdown- a brother will cook a large amount of food, and we'll bond together while having the roundtable.
      
    \subsection*{Supper Club}
      Each week, some of the older brothers choose a restaurant in the Greater Cleveland area. This lets us spend a bit of time outside of the Uptown bubble from campus, eat some new good food, and learn more about the local area.
      
  \section*{Super Smash Brothers Tournament}
    A few brothers of the most recent candidate class are launching a Super Smash Brothers Melee Tournament (the Nintendo, arcade-style video game) to raise money for the National Alliance on Mental Illness (NAMI). We will also be partnering with the Smash Club at CWRU, allowing Beta Nu to “smash stigma” associated with mental illness. The event will occur later in the semester.