\chapter{The Ritual}

  The past two semesters have shown increased application of our Ritual. Embodying the essence of the assisting hand and our sacred purpose as a chapter, Beta Nu organized and executed Mental Health Awareness Week during Fall 2014. It is due to MHA week, our ritual reviews, and our traditions that Greek Life awarded us an ``Excellent'' rating in the Ritual Pillar of Case Western Reserve’s Pytte Cup - CWRU’s Greek Life assessment application.

  \section*{Mental Health Awareness Week}
    As our application previously mentions, our last VPHS worked hard to address an issue on campus that affected more than just the Greek system: mental health. Our ritual clearly mentions that need for brothers to extend an assisting hand to those who need it. 
    
  \section*{Awards}
    In addition to the numerous awards and endowments given to us by IHQ, our own Greek Life Office at Case Western has recognized our efforts in ritual practice. The Agnar Pytte Cup annual chapter development evaluation and interview process found Theta Chi to demonstrate “Excellence” in the Ritual pillar, with specific laudations towards Alumni Relations, Membership Development, and Incorporation of Purpose. \\
    
    At this year's Initiation, we nominated brother James Fitzpatrick for the Colley award. Senior of the Year was also given to James Fitzpatrick in large part due to his labors for Mental Health Awareness Week. 
    
  \section*{Ritual Traditions}
    As IHQ knows, Beta Nu prides itself on ritual traditions during chapter. Specifically, Beta Nu holds ritual minutes during our Sunday chapter meetings in which a brother stands and gives his interpretation and application of a portion of the ritual. A sample ritual minute is attached for reference. \\
    
    This semester, we held Ritual Reviews and Traditions two weeks before Initiation on March 21. Flag Drop and Death of a Fraternity are staple traditions of Brotherhood Week, the week preceding Initiation; Flag Drop involves brothers holding up the fraternity flag and dropping it on account of a lack of brotherhood participation. Each brother in succession then picks up the flag on the promise to be a better brother. Death of Fraternity features a story following the disintegration of a Michigan chapter. Meanwhile, the ritual reviews involve readings of the ritual and discussions of its history and significance. The Chaplain and First Guard are in attendance at all ritual reviews to ensure the protection and secrecy of the ritual documents. We take very good care of our ritual and it is kept pristine. \\
    
    Initiation itself is held at a private on campus location. All active brothers are required to attend, barring extreme circumstances, and we are fortunate to have notable alumni and the brothers of the Beta Lambda chapter in attendance. This year, we had our 2009 Beta Nu Colley Award winner Daniel Neumann in attendance, along with Chase Nemeth and our chapter advisor, Dr. Richard Drushel. 
    
  \section*{Ceremonies}
    In addition to Initiation, we hold a Big Brother Ceremonies, New Member Ceremonies, and a Memorial Ceremony. We held two separate New Member Ceremonies this semester for our 5 initiated brothers, while we held one for all 7 initiated candidates last semester. The Fall Big Brother Ceremony is traditionally held at our annual OX Roast; however we held an additional ceremony at the Beta Nu house after the OX Roast. The Spring Big Brother Ceremony is held at the house. 
